%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://elijahwfeldman.com/}{\Large Elijah Feldman}} & Email: \href{mailto:eli@elijahwfeldman.com}{eli@elijahwfeldman.com}\\
  \href{https://elijahwfeldman.com/}{elijahwfeldman.com}
  \href{https://github.com/elijahfeldman7}{github.com/ElijahFeldman7}

\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thomas Jefferson High School for Science and Technology}{Alexandria, VA}
      {High School Diploma; GPA: 4.0}{Class of 2028}
      \resumeItemListStart
        \resumeItem{Coursework}{AP Biology, AP Computer Science, Research Statistics 1}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {George Mason University}{Fairfax, VA}
      {Research Intern}{June 2024 -- Present}
      \resumeItemListStart
        \resumeItem{LLM Finetuning}
          {
            Created a manually annotated 500+ sample dataset for parameter-efficient finetuning of an 8-billion parameter language model. Achieved a 25\% performance improvement over a LLaMA 70B baseline in relationship and entity extraction tasks for legal court filings.
          }
        \resumeItem{High-Performance Computing (HPC)}
          {
            Ran training pipelines and evaluation metrics on A100 80GB GPU clusters using Slurm to send experiment jobs. Used Ollama for local model deployment and testing.
          }
        \resumeItem{Empirical Evaluation \& Data Analysis}
          {
            Evaluated the fine-tuned model against both the model prior to fine-tuning and another baseline over thirty trials. Conducted rigorous statistical analyses to establish normality, correct for covariance, and validate statistical significance across trials.
          }
      \resumeItemListEnd

    \resumeSubheading
      {TJ Computer Systems Lab}{Alexandria, VA}
      {Systems Administrator}{Aug 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Infrastructure Management}
          {
            Maintained 30+ Debian-based workstations supporting a user base of over 60 students and faculty. Deployed and managed a web-based UI infrastructure enabling remote desktop access for 50+ concurrent users.
          }
        \resumeItem{Cluster Administration}
          {
            Maintained a 50+ node compute cluster. Deployed containerized virtual environments and optimized high-performance compute resources for the neuroscience laboratory.
          }
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Watermarking Diffusion Language Models}
      {Independent project mentored by a George Mason University faculty member involving the creation of a robust method for applying a watermark to diffusion language model generated text.}
    \resumeSubItem{\href{https://bioblitz.net}{BioBlitz}}
      {
        Built and deployed a full-stack educational web platform serving 300+ active users with over 1000 completed assessments for MCAT or Biology Olympiad preparation. Implemented a recommendation system and Elo-based scoring algorithm. Utilized A/B testing to optimize platform analytics and user engagement.
      }
  \resumeSubHeadingListEnd

\section{Awards \& Honors}
    \resumeSubHeadingListStart
        \resumeSubItem{American Invitational Mathematics Examination (AIME)}{Qualifier \& AMC 10 Honor Roll (Top 2.5\%)}
        \resumeSubItem{United States of America Computing Olympiad (USACO)}{Gold Division (Top $\sim$5\% globally)}
        \resumeSubItem{United States of America Biology Olympiad (USABO)}{2x Honorable Mention (Top 20\% nationally)}
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming \& Markup}{: Python, Java, JavaScript, LaTeX, HTML/CSS}
   }
   \item{
     \textbf{ML \& Data Libraries}{: Hugging Face, scikit-learn, NumPy, pandas}
   }
   \item{
     \textbf{Tools \& Frameworks}{: Linux, Slurm, Ollama, Git, React}
   }
   \item{
     \textbf{Core Competencies}{: High-Performance Computing (HPC), System Administration, Knowledge Graphs, Statistical Data Analysis}
   }
 \resumeSubHeadingListEnd

\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{FineREX: Fine-Tuned NER-RE for Human Smuggling Knowledge Graphs}
      {
        Elijah Feldman, Dipak Meher, Carlotta Domeniconi. Under Review, ICKG 2026. \href{https://arxiv.org/abs/2606.19710}{arXiv:2606.19710}
      }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
